Arrival Management with Open Data

### 2023-02-28 data-analytics.qmd
associated landing runway (first stab)

```{r setup, include=FALSE}
library(tidyverse)
```

@@

> ds |> filter(grepl(pattern = "^BAW", x = FLTID ), ALT_B < 1000) |> distinct(FLTID)
# A tibble: 761 × 1
   FLTID  
   <chr>  
 1 BAW112B
 2 BAW32  
 3 BAW237 
 4 BAW236 
 5 BAW16  
 6 BAW28  
 7 BAW34  
 8 BAW56  
 9 BAW262 
10 BAW74

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)

ggplot2::theme_set(ggplot2::theme_minimal())
```

@@

@@

show temporal and vertical profile

```{r}
ggplot(data = baws |> filter(FLTID %in% picks)) +
  geom_point(aes(x = TIME, y = ALT_B, color = FLTID), size = 0.3)
```

save out some test trajectories

write_csv(baws |> filter(FLTID %in% picks), file = "./data/tst-egll-baw.csv.gz")

airport arrival box

```{r}

```

### 2023-02-28 paper.qmd
associated landing runway (first stab)

## Open Data for Operational Performance Monnitoring

>>>>

The identification of the landing direction is based on a simple geospatial heuristic.
Conceptually, aircraft are aligned with the runway (centerline) before landing.
An aircraft is assigned to a landing runway based on the closeness of its pre-landing positions to the extended runway centerline.

## Open Data for Operational Performance Monitoring
